### 2023-02-10 doc/manuscript/translocation.qmd
Additional edits to comments in introduction

-   <!--# Zooming out here to make a broader point --> Few, if any, studies of disease-impacted species have provided comprehensive evidence that (1) evolutionary rescue can increase host resistance, (2) increased host resistance contributes to higher individual fitness (e.g., survival) in the presence of disease and allows population growth, (3) higher individual fitness and positive population growth applies beyond the natal environment, (4) individuals from higher-fitness populations can be used in translocations to reestablish extirpated populations, and (5) many reestablished populations have a high probability of persisting over the long term in a landscape of disease. <!--# I don't know how many of these boxes we can check, but they seem like important points to help us lay the foundation for our study (which checks more of these boxes than do most studies). I actually wonder if taking the broader approach outlined in this bullet would make for a more compelling argument than one focused more narrowly on issue #3, as most of the bullets in this paragraph currently do. That issue, although important, may distract from the broader perspective that I tried to highlight. -->

P4: Description of MYL frog species complex, impacts of Bd, and evidence of recent recovery. Cite Knapp et al. (2016) to emphasize that frogs in recovering populations are more resistant to Bd than those in Bd-naive populations.

>>>>

-   <!--# Zooming out here to make a broader point --> Few, if any, studies of disease-impacted species have provided comprehensive evidence that (1) evolutionary rescue can increase host resistance, (2) increased host resistance contributes to higher individual fitness (e.g., survival) in the presence of disease and allows population growth, (3) higher individual fitness and positive population growth applies beyond the natal environment, (4) individuals from higher-fitness populations can be used in translocations to reestablish extirpated populations, and (5) many reestablished populations have a high probability of persisting over the long term in a landscape of disease. <!--# I don't know how many of these boxes we can check convincingly, but they seem like important points to help us lay the foundation for our study (which checks more of these boxes than do most studies). I actually wonder if taking the broader approach outlined in this bullet would make for a more compelling argument than one focused more narrowly on issue #3, as most of the bullets in this paragraph currently do. That issue, although important, may distract from the broader perspective that I tried to highlight. -->

P4: Description of MYL frog species complex, impacts of Bd, and evidence of recent recovery. Cite Knapp et al. (2016) to emphasize that frogs in recovering populations are less susceptible to Bd than those in Bd-naive populations.
